\documentclass[lualatex]{beamer}

%\usepackage[russian,english]{babel}
\usepackage{graphicx}
\usepackage{comment}
\usetheme{deepblue}


\title
    {日本語テスト \\ Japanese trials}
\subtitle
    {サンプルプレゼンテーション \\ using beamer-modern template}
\author
    {南 浩人 \\ Hiroto Minami}

\setbeamertemplate{blocks}[rounded][shadow=true]

\begin{document}

    \frame[plain]{\titlepage}

    \frame{\tableofcontents}

    \section{Hello world}

    \begin{frame}{Hello world}
        こんにちは世界！ \\
        よい{\bf 世界}です！ \\
        Hello world! One morning, when \textbf{Gregor Samsa}
        woke from troubled dreams, he found himself
        transformed in his bed into a horrible vermin.
        He lay on his armour-like back, and if he
        lifted his head a little he could see his brown
        belly, slightly domed and divided by arches
        into \textit{stiff sections}. The bedding was hardly
        able to cover it and seemed ready to slide off
        any moment. His many legs, pitifully thin
        compared with the size of the rest of him,
        waved about helplessly as he looked. "What's
        happened to me?" he thought. It wasn't a dream.
    \end{frame}

%    \section{Hello lists}

    \begin{frame}{Hello itemize}
        \begin{itemize}
            \item Item 1
            \item Item 2
            \item Item 3
        \end{itemize}
    \end{frame}

    \begin{comment}
    \begin{frame}{Hello enumerate}
        \begin{enumerate}
            \item Item 1
            \item Item 2
            \item Item 3
        \end{enumerate}
    \end{frame}
\end{comment}


%    \section{Hello math}

    \begin{frame}{Hello math}
        $$ \sum_{n=1}^\infty \frac{1}{2^n} = 2 $$
    \end{frame}

%    \section{Hello tables}

    \begin{frame}{Hello tables}
        \centering
        \begin{tabular}{|c|c|c|}
            \hline
            Name & Age & Score \\
            \hline
            John & 10 & 100 \\
            Alex & 11 & 85 \\
            Ann  & 9  & 80 \\
            \hline
        \end{tabular}
    \end{frame}

%    \section{Hello blocks}

    \begin{frame}{Hello blocks}
        \begin{block}{Block title}[shadow=true]
            日本語
        \end{block}

        \begin{exampleblock}{Block title}
            This is an example block
        \end{exampleblock}

        \begin{alertblock}{Block title}
            テスト
        \end{alertblock}
    \end{frame}

\end{document}
